---
title: "U.S. Lobbying Practices"
date:  05/05/2020
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```


## Group I: Money in Politics: Elliott Tran, Julia Tache and Sayali Nagwekar {.tabset}

### Overview

We are interested in exploring lobbying reports submitted in compliance with the U.S. Lobbying Disclosure Act of 1995 (LDA) to find insights on how money influences the political process. Utilizing 7 datasets regarding LDA from Open Secrets, we will explore the unique structures and relationships of lobbying in politics. We decided to examine lobbying efforts, key players, and the effects lobbying has on legislation and compare state sponsors and issues between 2018-2019 and the election years of 2015-2016.

Scroll over on the chart below to see stats for the number of lobbying reports, the number of clients, and the number of lobbyists over the past 5 years.

```{r packages and data}

library(shiny)
library(tidytext)
library(SnowballC)
library(wordcloud)
library(lsa)
library(tidyverse)
library(httr)
library(dygraphs)
library(tigris)
library(leaflet)
library(maps)
library(ggmap)
library(viridis)
library(visNetwork)
library(networkD3)
library(htmlwidgets)
library(shinythemes)
library(dygraphs)
library(network)
library(ggthemes)
options(tigris_use_cache = TRUE)

lob_issue <- read_csv("./data/lob_issue.txt", quote ="|,|",
                      col_names = FALSE)
lob_issue <- plyr::rename(lob_issue, c('X1' = "SI_ID", "X2" = "Uniqid", 
                                       "X3" = "IssueID", "X4" = "Issue", 
                                       "X5" = "SpecificIssue", "X6" = "Year"))

lob_lobbying <- read_csv("./data/lob_lobbying.txt", quote ="|,|",
                         col_names = FALSE)

lob_lobbying <- plyr::rename(lob_lobbying, c('X1' = "Uniqid", "X2" = "Registrant_raw", 
                                             "X3" = "Registrant", "X4" = "Isfirm", 
                                             "X5" = "Client_raw", "X6" = "Client", "X7" = "Ultorg", 
                                             "X8" = "Amount", "X9" = "Catcode", "X10" = "Source", 
                                             "X11" = "Self", "X12" = "IncludeNSFS", "X13" = "Use", 
                                             "X14" = "Ind", "X15" = "Year", "X16" = "Type", 
                                             "X17" = "Typelong", "X18" = "Affiliate"))

lob_lobbyist <- read_csv("./data/lob_lobbyist.txt", quote ="|,|",
                         col_names = FALSE)
lob_lobbyist <- plyr::rename(lob_lobbyist, c('X1' = "Uniqid", "X2" = "Lobbyist_raw", 
                                             "X3" = "Lobbyist", "X4" = "Lobbyist_id", 
                                             "X5" = "Year", "X6" = "OfficialPosition", "X7" = "CID", 
                                             "X8" = "Formercongmem"))

lob_bills <- read_csv("./data/lob_bills.txt", quote ="|,|",
                      col_names = FALSE)

lob_bills <- rename(lob_bills, c("B_ID" = "X1", "SI_ID" = "X2", 
                                 "CongNo" = "X3", "Bill_Name" = "X4"))

```

```{r time series}
# Time Series

open_secrets <- inner_join(lob_lobbying, lob_lobbyist, by = c('Uniqid', 'Year')) 

open_secrets <- open_secrets %>%
  select(Year, Uniqid, Lobbyist_id, Client) %>%
  filter(Year >= 2015)
  
ts_report <- open_secrets %>%
  select(Uniqid, Year) %>%
  distinct(Uniqid, .keep_all = TRUE) %>%
  mutate(Uniqid = 1) %>%  
  group_by(Year) %>% 
  summarise_each(funs(sum)) %>%
  rename("Number of Lobbying Reports" = "Uniqid")

ts_lobbyists <- open_secrets %>%
  select(Lobbyist_id, Year) %>%
  distinct(Lobbyist_id, .keep_all = TRUE) %>%
  mutate(Lobbyist_id = 1) %>%  
  group_by(Year) %>% 
  summarise_each(funs(sum)) %>%
  rename("Number of Lobbyists" = "Lobbyist_id")

ts_clients <- open_secrets %>%
  select(Client, Year) %>%
  distinct(Client, .keep_all = TRUE) %>%
  mutate(Client = 1) %>%  
  group_by(Year) %>% 
  summarise_each(funs(sum)) %>%
  rename("Number of Clients" = "Client")

time_seriesg <- full_join(ts_clients, ts_lobbyists, by = "Year") 

time_seriesg <- full_join(ts_report, time_seriesg, by = "Year")

time_seriesg$Year <- as.single(time_seriesg$Year)

dygraph(time_seriesg, main = "U.S. Lobbying Landscape in the Last 5 Years") %>%
  dyOptions(digitsAfterDecimal = 0, strokeWidth = 3, colors = RColorBrewer::brewer.pal(3, "Set2")) %>%
  dyLegend(show = "follow", width = "200")
```

### By Lobbyist

**Where do the top out-of-house lobbyists work? (2019)**

Top lobbyists were determined by the amount spent in lobbying efforts connected to their name in 2019.

```{r sna 1}
# Social Network Analysis

merge_df <- inner_join(lob_lobbying, lob_issue, by = c("Uniqid","Year"))
merge_df2 <- inner_join(merge_df, lob_lobbyist, by = c("Uniqid","Year"))

df_2019 <- merge_df2 %>% 
  filter(Year == 2019)  

names2019 <- df_2019 %>%
  select(Lobbyist_id, Lobbyist, Issue, Registrant, Client, Uniqid) %>%
  dplyr::distinct(Uniqid, .keep_all = TRUE)

agg2019_lobby <- df_2019 %>%
  dplyr::select(Uniqid, Amount) 

agg2019_lobby <- aggregate(. ~ Uniqid, data = agg2019_lobby, FUN = sum)

agg2019_lobby <- full_join(names2019, agg2019_lobby, by = "Uniqid")

## By Lobbyist

names2019_2 <- df_2019 %>%
  select(Lobbyist_id, Lobbyist, Registrant, Client) %>%
  dplyr::distinct(Lobbyist_id, .keep_all = TRUE)

agg2019_lobby2 <- df_2019 %>%
  filter(Isfirm == "y") %>%
  dplyr::select(Lobbyist_id, Amount) 

agg2019_lobby2 <- aggregate(. ~ Lobbyist_id, data = agg2019_lobby2, FUN = sum)

agg2019_lobby2 <- full_join(names2019_2, agg2019_lobby2, by = "Lobbyist_id") 

agg2019_lobbyist <- agg2019_lobby2 %>%
  select(Lobbyist_id, Amount) %>%
  group_by(Lobbyist_id) %>%
  summarise_each(funs(if(is.numeric(.)) sum(., na.rm = TRUE) else first(.)))

agg2019_lobbyist <- left_join(agg2019_lobbyist, agg2019_lobby2, by = "Lobbyist_id") 

agg2019_lobbyist <- top_n(agg2019_lobbyist, 50, wt = Amount.x)

lobby_id <- agg2019_lobbyist %>%
  distinct(Lobbyist) %>%
  dplyr::rename(label = Lobbyist)

registrant <- agg2019_lobbyist %>%
  distinct(Registrant) %>%
  dplyr::rename(label = Registrant)

nodes <- full_join(lobby_id, registrant, by = "label") %>% 
  rowid_to_column("id")

lobby_issue <- agg2019_lobbyist %>%  
  group_by(Lobbyist, Registrant) %>%
  dplyr::summarise(weight = n()) %>% 
  ungroup()

edges <- lobby_issue %>% 
  left_join(nodes, by = c("Lobbyist" = "label")) %>% 
  dplyr::rename(from = id)

edges <- edges %>% 
  left_join(nodes, by = c("Registrant" = "label")) %>% 
  dplyr::rename(to = id)

edges <- select(edges, from, to, weight)

nodes_d3 <- mutate(nodes, id = id - 1)

edges_d3 <- mutate(edges, from = from - 1, to = to - 1)

sankeyNetwork(Links = edges_d3, Nodes = nodes_d3, Source = "from", Target = "to", 
              NodeID = "label", Value = "weight", unit = "Lobbied For", iterations = 100,
              fontSize=16, width=1500, height=1500,
              margin = list("left"=100))
```

**Mapping out Congressmen-turned-Lobbyists by State**

A look at how many former congressmen were or became lobbyists and which states they came from.

```{r gis former congressmen}

congressmen <- read_csv("./data/legislators-historical.csv")

congressmen$name <- paste(congressmen$last_name, congressmen$first_name, sep = ", ")

former_congressmen <- lob_lobbyist %>% filter(Formercongmem == "y")

former_congressmen <- former_congressmen %>%
  rename("name" = "Lobbyist")

full_congressmen <- left_join(former_congressmen, congressmen)

full_congressmen <- full_congressmen %>% 
  select(name, birthday, state, district, party) %>%
  distinct()

number_congressmen <- full_congressmen %>% group_by(state) %>%
  summarize(`Number of Congressmen/State` = n())

states <- states(cb = FALSE)

states_merged_congressmen <- geo_join(states, number_congressmen, "STUSPS", "state") 
states_merged_congressmen <- na.omit(states_merged_congressmen)

pal <- colorNumeric("plasma", domain = states_merged_congressmen$`Number of Congressmen/State`)

labels <- sprintf("<strong>%s</strong><br/>%g Former Congressmen turned Lobbyists",
                  states_merged_congressmen$NAME,
                  states_merged_congressmen$`Number of Congressmen/State`) %>% 
  lapply(htmltools::HTML)

css_fix <- "div.info.legend.leaflet-control br {clear: both;}" # CSS to correct spacing of legend
html_fix <- htmltools::tags$style(type = "text/css", css_fix)  # Convert CSS to HTML

leaflet(states_merged_congressmen) %>%
  setView(-98.483330, 38.712046, zoom = 4) %>% 
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(fillColor = ~pal(states_merged_congressmen$`Number of Congressmen/State`), 
              weight = 0.5, 
              opacity = 1, 
              color = "black",
              dashArray = "1",
              fillOpacity = 1, 
              smoothFactor = 0.2, 
              highlight = highlightOptions(weight = 5, 
                                           color = "white",
                                           dashArray = "",
                                           bringToFront = TRUE),
              label = labels,
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"),
                                          textsize = "15px", 
                                          direction = "auto")) %>%
  addLegend(title = "No. of Congressmen/State", 
            pal = pal, 
            values = states_merged_congressmen$`Number of Congressmen/State`, 
            position = "bottomright") %>% 
  htmlwidgets::prependContent(html_fix) 
```

### By Lobbying Client

**What are the top lobbying clients lobbying for? (2019)**

Top clients were determined by the amount spent in lobbying efforts connected to their name in 2019.

```{r sna 2}

## By Client

agg2019_client <- agg2019_lobby %>%
  select(Client, Amount) %>%
  group_by(Client) %>%
  summarise_each(funs(if(is.numeric(.)) sum(., na.rm = TRUE) else first(.))) %>%
  top_n(25, wt = Amount)

agg2019_client <- left_join(agg2019_client, agg2019_lobby, by = "Client") 

lobby_id2 <- agg2019_client %>%
  distinct(Client) %>%
  dplyr::rename(label = Client)

issue2 <- agg2019_client %>%
  distinct(Issue) %>%
  dplyr::rename(label = Issue)

nodes2 <- full_join(lobby_id2, issue2, by = "label") %>% 
  rowid_to_column("id")

lobby_issue2 <- agg2019_client %>%  
  group_by(Client, Issue) %>%
  dplyr::summarise(weight = n()) %>% 
  ungroup()

edges2 <- lobby_issue2 %>% 
  left_join(nodes2, by = c("Client" = "label")) %>% 
  dplyr::rename(from = id)

edges2 <- edges2 %>% 
  left_join(nodes2, by = c("Issue" = "label")) %>% 
  dplyr::rename(to = id)

edges2 <- select(edges2, from, to, weight)

nodes_d3_2 <- mutate(nodes2, id = id - 1)

edges_d3_2 <- mutate(edges2, from = from - 1, to = to - 1)

sankeyNetwork(Links = edges_d3_2, Nodes = nodes_d3_2, Source = "from", Target = "to", 
              NodeID = "label", Value = "weight", unit = "Lobbied For", iterations = 100,
              fontSize=16, width=1000, height=1000,
              margin = list("left"=100))

```

**Text Analysis of the Clients' Industries**

```{r nlp}

library(textdata)

lobby2 <- tibble(file = paste0(c("./data/lob_indus.txt"))) %>%
        mutate(text = purrr::map(file, read_lines)) %>%
        unnest() %>%
        group_by(file = str_sub(basename(file), 1, -5)) %>% 
        mutate(line_number = row_number()) %>%
        ungroup() %>%
        unnest_tokens(word, text) %>% 
        anti_join(stop_words) %>% ## remove stop words 
        mutate(word = wordStem(word)) ## stemming the words

lobby2_sentiment <- lobby2 %>%
        inner_join(get_sentiments("bing")) %>%
        count(word, sentiment, sort = TRUE) %>%
        ungroup()

lobby2_sentiment <- lobby2_sentiment %>%
        group_by(sentiment) %>%
        top_n(10) %>%
        ungroup() %>%
        mutate(word = reorder(word, n)) %>%
        ggplot(aes(word, n, fill = sentiment)) +
        geom_col(show.legend = FALSE) +
        facet_wrap(~sentiment, scales = "free_y") +
        labs(y = "Contribution to sentiment",
                x = NULL, title = "Positive and Negative Sentiment by Lobbying Industry") +
        coord_flip()

lobby2_sentiment

nrc_disgust <- get_sentiments("nrc") %>% 
        filter(sentiment == "disgust")

sent2_disgust <- lobby2 %>%
        inner_join(nrc_disgust) %>%
        count(word, sort = TRUE)


sent2_disgust <- sent2_disgust %>%
  group_by(n) %>%
  top_n(10) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = n)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~n, scales = "free_y") +
  labs(y = "Contribution to sentiment",
       x = NULL, title = "NRC Disgust Sentiment by Lobbying Industry") +
  theme(axis.text = element_text(size = 5)) +
  coord_flip()

sent2_disgust

```
      
### By Bills and Issues

There are generally more bills sponsored through lobbying during the election year possibly because the passage of new laws in favor of certain constituencies could lead voters to support politicians who may be friendly to lobbying interests. Given the unique nature of the 2016 election, new bills may have been proposed which would have attempted to make President Donald Trump easier or harder to re-elect, to limit his powers, help or hurt his agenda, etc. Let's look at how many bills per state were sponsored through lobbying efforts and the top issues which bills covered.

**Bills sponsored by lobbying 2015-2016**

```{r gis bills sponsored 15-16}

css_fix <- "div.info.legend.leaflet-control br {clear: both;}" # CSS to correct spacing of legend
html_fix <- htmltools::tags$style(type = "text/css", css_fix)  # Convert CSS to HTML

bills_issues <- left_join(lob_bills, lob_issue) %>% 
  distinct(Bill_Name, .keep_all = TRUE) 

bills_114 <- read_csv("./data/114 Bills.csv")

bills_114$Sponsor <- as.character(str_extract_all(bills_114$Sponsor, "[A-Z]{2}"))

bills_114 <- bills_114 %>% rename("Bill_Name" = "Legislation Number")

bills_114$Bill_Name <- str_replace_all(bills_114$Bill_Name, "\\s+", "")

lob_bills_full_15_16 <- inner_join(bills_114, bills_issues) %>% 
  distinct(Bill_Name, .keep_all = TRUE)

lob_states_15_16 <- lob_bills_full_15_16 %>% group_by(Sponsor) %>%
  summarize(`Number of Bills/State` = n()) 

states_merged_15_16 <- geo_join(states, lob_states_15_16, "STUSPS", "Sponsor") 
states_merged_15_16 <- na.omit(states_merged_15_16)

pal <- colorNumeric("plasma", domain = states_merged_15_16$`Number of Bills/State`)

labels <- sprintf("<strong>%s</strong><br/>%g Bills Sponsored",
                  states_merged_15_16$NAME, states_merged_15_16$`Number of Bills/State`) %>% 
  lapply(htmltools::HTML)

leaflet(states_merged_15_16) %>%
  setView(-98.483330, 38.712046, zoom = 4) %>% 
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(fillColor = ~pal(states_merged_15_16$`Number of Bills/State`), 
              weight = 0.5, 
              opacity = 1, 
              color = "black",
              dashArray = "1",
              fillOpacity = 1, 
              smoothFactor = 0.2, 
              highlight = highlightOptions(weight = 5, 
                                           color = "white",
                                           dashArray = "",
                                           bringToFront = TRUE),
              label = labels,
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"),
                                          textsize = "15px", 
                                          direction = "auto")) %>%
  addLegend(title = "No. of Bills/State 2015-2016", 
            pal = pal, 
            values = states_merged_15_16$`Number of Bills/State`, 
            position = "bottomright")
```

**Top issues in bills sponsored by lobbying 2015-2016**

```{r top issues 15-16}
lob_issues_15_16 <- lob_bills_full_15_16 %>% 
  group_by(Sponsor, Issue) %>%
  summarize(`Number of Bills` = n()) %>%
  group_by(Sponsor) %>%
  arrange(`Number of Bills`) %>%  
  filter(`Number of Bills` %in% range(`Number of Bills`)) %>% 
  group_by(Sponsor) %>%
  arrange(`Number of Bills`) %>%
  # in case of ties
  slice(if (length(`Number of Bills`) == 50) 50 else c(50, n())) 

states_merged_15_16 <- geo_join(states, lob_issues_15_16, "STUSPS", "Sponsor") 
states_merged_15_16 <- na.omit(states_merged_15_16)

pal <- colorNumeric("plasma", domain = states_merged_15_16$`Number of Bills`)

labels <- sprintf("<strong>%s</strong><br/><strong>%s</strong><br/>%g Bills Sponsored",
                  states_merged_15_16$NAME,
                  states_merged_15_16$Issue, states_merged_15_16$`Number of Bills`) %>% 
  lapply(htmltools::HTML)

leaflet(states_merged_15_16) %>%
  setView(-98.483330, 38.712046, zoom = 4) %>% 
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(fillColor = ~pal(states_merged_15_16$`Number of Bills`), 
              weight = 0.5, 
              opacity = 1, 
              color = "black",
              dashArray = "1",
              fillOpacity = 1, 
              smoothFactor = 0.2, 
              highlight = highlightOptions(weight = 5, 
                                           color = "white",
                                           dashArray = "",
                                           bringToFront = TRUE),
              label = labels,
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"),
                                          textsize = "15px", 
                                          direction = "auto")) %>%
  addLegend(title = "No. of Bills 2015-2016", 
            pal = pal, 
            values = states_merged_15_16$`Number of Bills`, 
            position = "bottomright")
```

**Bills sponsored by lobbying 2018-2019**

```{r gis bills sponsored 18-19}
# Bills

bills_full_18_19 <- read_csv("./data/115 Bills.csv")

bills_full_18_19$Sponsor <- as.character(str_extract_all(bills_full_18_19$Sponsor, "[A-Z]{2}"))

bills_full_18_19 <- bills_full_18_19 %>% rename("Bill_Name" = "Legislation Number")

bills_full_18_19$Bill_Name <- str_replace_all(bills_full_18_19$Bill_Name, "\\s+", "")

lob_bills_full_18_19 <- inner_join(bills_full_18_19, bills_issues) %>% 
  distinct(Bill_Name, .keep_all = TRUE)

lob_states_18_19 <- lob_bills_full_18_19 %>% group_by(Sponsor) %>%
  summarize(`Number of Bills/State` = n())

states_merged_18_19 <- geo_join(states, lob_states_18_19, "STUSPS", "Sponsor") 
states_merged_18_19 <- na.omit(states_merged_18_19)

pal <- colorNumeric("plasma", domain = states_merged_18_19$`Number of Bills/State`)

labels <- sprintf("<strong>%s</strong><br/>%g Bills Sponsored",
                  states_merged_18_19$NAME, states_merged_18_19$`Number of Bills/State`) %>% 
  lapply(htmltools::HTML)

leaflet(states_merged_18_19) %>%
  setView(-98.483330, 38.712046, zoom = 4) %>% 
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(fillColor = ~pal(states_merged_18_19$`Number of Bills/State`), 
              weight = 0.5, 
              opacity = 1, 
              color = "black",
              dashArray = "1",
              fillOpacity = 1, 
              smoothFactor = 0.2, 
              highlight = highlightOptions(weight = 5, 
                                           color = "white",
                                           dashArray = "",
                                           bringToFront = TRUE),
              label = labels,
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"),
                                          textsize = "15px", 
                                          direction = "auto")) %>%
  addLegend(title = "No. of Bills/State 2018-2019", 
            pal = pal, 
            values = states_merged_18_19$`Number of Bills/State`, 
            position = "bottomright")
```

**Top issues in bills sponsored by lobbying 2018-2019**

```{r gis top issues 18-19}
lob_issues_18_19 <- lob_bills_full_18_19 %>% 
  group_by(Sponsor, Issue) %>%
  summarize(`Number of Bills` = n()) %>%
  group_by(Sponsor) %>%
  arrange(`Number of Bills`) %>%  
  filter(`Number of Bills` %in% range(`Number of Bills`)) %>% 
  group_by(Sponsor) %>%
  arrange(`Number of Bills`) %>%
  # in case of ties
  slice(if (length(`Number of Bills`) == 50) 50 else c(50, n())) 

states_merged_18_19 <- geo_join(states, lob_issues_18_19, "STUSPS", "Sponsor") 
states_merged_18_19 <- na.omit(states_merged_18_19)

pal <- colorNumeric("plasma", domain = states_merged_18_19$`Number of Bills`)

labels <- sprintf("<strong>%s</strong><br/><strong>%s</strong><br/>%g Bills Sponsored",
                  states_merged_18_19$NAME,
                  states_merged_18_19$Issue, states_merged_18_19$`Number of Bills`) %>% 
  lapply(htmltools::HTML)

leaflet(states_merged_18_19) %>%
  setView(-98.483330, 38.712046, zoom = 4) %>% 
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(fillColor = ~pal(states_merged_18_19$`Number of Bills`), 
              weight = 0.5, 
              opacity = 1, 
              color = "black",
              dashArray = "1",
              fillOpacity = 1, 
              smoothFactor = 0.2, 
              highlight = highlightOptions(weight = 5, 
                                           color = "white",
                                           dashArray = "",
                                           bringToFront = TRUE),
              label = labels,
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"),
                                          textsize = "15px", 
                                          direction = "auto")) %>%
  addLegend(title = "No. of Bills 2018-2019", 
            pal = pal, 
            values = states_merged_18_19$`Number of Bills`, 
            position = "bottomright")
```

[Click for information about the Dataset](https://www.opensecrets.org/federal-lobbying/methodology)

[Process Book](https://drive.google.com/open?id=1bm3iycbE_5RC8SAwTj41A5_IIITi-45e)

[Code Files](https://drive.google.com/open?id=1a12htA6JheAVKNCVe9BkwpOqxb_l5Z7k)
